### 2018-02-17 doc/manuscript.Rmd
reference appropriate results dataframes

pls_gee <- project_data %>%
    analyze_gee(
        x = c('Comp1', 'Comp2'),
        data_prep = 'pls',
        pls_results = pls_results$pls_isi_df
        ) %>% 
    dplyr::select(Yterms, Xterms, estimate, p.value) %>% 
    dplyr::filter(Xterms == 'Comp1') %>% 
    dplyr::mutate(p.value = aide::format_pval(p.value),
                  estimate = aide::format_round(estimate))
```

@@

tagfa <- calc_tagfa_percent()
outcome_chg <- calc_outcome_changes()
female <- calc_discr_npct(ds0yr$Sex, 'Female')
euro <- calc_discr_npct(ds0yr$Ethnicity, 'European')
fhd <- calc_discr_npct(ds0yr$FamHistDiab, 'Yes')
est0 <- calc_gee_estci(gee_unadj_df)
est1 <- calc_gee_estci(gee_adj_df)
fa_cor <- calc_cor(cor_df)
fa_cor_mol <- calc_cor(cor_df_mol)
cor_pls_homa2 <- calc_pred_corr(pls_homa2_t, pls_homa2_t$test_data)
cor_pls_isi <- calc_pred_corr(pls_isi_t, pls_isi_t$test_data)
cor_pls_igi <- calc_pred_corr(pls_igi_t, pls_igi_t$test_data)
cor_pls_issi2 <- calc_pred_corr(pls_issi2_t, pls_issi2_t$test_data)
```

>>>>

pls_gee <- project_data %>%
    analyze_gee(
        x = c('Comp1', 'Comp2'),
        data_prep = 'pls',
        pls_results = pls_results$isi
        ) %>% 
    dplyr::select(Yterms, Xterms, estimate, p.value) %>% 
    dplyr::filter(Xterms == 'Comp1') %>% 
    dplyr::mutate(p.value = aide::format_pval(p.value),
                  estimate = aide::format_round(estimate))
```

@@

tagfa <- calc_tagfa_percent()
outcome_chg <- calc_outcome_changes()
female <- calc_discr_npct(ds0yr$Sex, 'Female')
euro <- calc_discr_npct(ds0yr$Ethnicity, 'European')
fhd <- calc_discr_npct(ds0yr$FamHistDiab, 'Yes')
gmest0 <- calc_gee_estci(gee_results$unadj)
gmest1 <- calc_gee_estci(gee_results$adj)
fa_cor <- calc_cor(cor_results$conc)
fa_cor_mol <- calc_cor(cor_results$pct)
cor_pls_homa2 <- calc_pred_corr(pls_homa2_t, pls_homa2_t$test_data)
cor_pls_isi <- calc_pred_corr(pls_isi_t, pls_isi_t$test_data)
cor_pls_igi <- calc_pred_corr(pls_igi_t, pls_igi_t$test_data)
cor_pls_issi2 <- calc_pred_corr(pls_issi2_t, pls_issi2_t$test_data)
```
